---
title: "Data Acquisition and Management Weekly Assignment - wk9"
author: "Chun San Yip"
date: "2020/03/29"
output: html_document
---
  
Overview:
The assignment for this week is related to API. 
The task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.
The New York Times web site provides a rich set of APIs, as described here:https://developer.nytimes.com/apis 
I need to start by signing up for an API key.

Load all the required packages.
```{r load-packages, message = FALSE}
library(tidyverse)
library(httr)
library(jsonlite)
```

Search the Movies API by "Star Wars"
```{r}
jStar <- "https://api.nytimes.com/svc/movies/v2/reviews/search.json?query=star wars&api-key=xKfN6XkV5Uzt3DzbxpuGuP6tw7DAr4oD"

#Use httr Request
m <- GET(jStar)

#Extract content from a request
jM <- content(m, "parse")

#Convert the list to a dataframe 
jF <- data.frame(t(sapply((jM[[5]]), c)))

#Something is wrong with the jF dataframe as each "field" is still a list, I have to convert by usinng the view function
jFmodify <- view(jF)

jFmodify
          
```